\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-23 pldi/draft.tex
Remove third use case from intro

We evaluate \sys using
  (i) a series of benchmarks, ranging from classic one-liners found in the \unix literature to modern data-processing pipelines;
  (ii) three large and complex use cases, covering temperature analysis, web crawling and indexing, and container orchestration; and
  (iii) a series of targeted micro-benchmarks inspired by (and comparing with) possible alternatives.
The results demonstrate significant advantages in \todo{correctness},
\todo{manual effort}, and performance---with \sys offering an order-of-magnitude performance improvements due to its transformations and optimized runtime.
%% ---with \sys's transformations offering an order-of-magnitude performance improvements aided further by \sys's optimized runtime components.
Naturally, these improvements depend on several factors such as the script's execution time, the pipeline depth, and the parallelizability class under which a command falls. 
%\kk{Do we need to mention this last sentence here? Without context it is pretty difficult for anyone to get something out of it.}

@@

The core of \sys is an abstract dataflow graph (DFG) model that is used as the intermediate representation on which \sys performs optimizations.
%% representation that is expressive enough to model data parallelism in shell programs.
%% support a large subset of shell programs.\nv{Immediate Q: How Large? Which programs are not supported? Why?}
\sys first lifts sections of the input script to the DFG
representation, it performs transformations to expose parallelism, and
then instantiates each DFG back to a parallel shell script.  A
fundamental difference with other DFG models is that it encodes the
order in which a node reads its inputs, which in turn enables a set of
graph transformations that can be iteratively applied to expose
parallelization opportunities for \tsta and \tpur commands.
%% data parallelism as task parallelism.\nv{What does this mean? What if they are fundamentally different in the reivewer's mind? Example?}
%% These transformations can then be applied in an iterative way, optimizing the program to utilize available computational resources. 
In \Cref{graph-components} we define the DFG model and describe the
correspondence with shell scripts, and in \Cref{ir:transformations} we
describe the graph transformations and \todo{give intuition about their
correctness}.

>>>>

We evaluate \sys using
  (i) a series of benchmarks, ranging from classic one-liners found in the \unix literature to modern data-processing pipelines;
(ii) two large and complex use cases, covering temperature analysis, and web
%% crawling and
indexing;
%% , and container orchestration;
and (iii) a series of targeted micro-benchmarks inspired by (and
comparing with) possible alternatives.  The results demonstrate
significant advantages in \todo{correctness}, \todo{manual effort},
and performance---with \sys offering an order-of-magnitude performance
improvements due to its transformations and optimized runtime.
%% ---with \sys's transformations offering an order-of-magnitude performance improvements aided further by \sys's optimized runtime components.
Naturally, these improvements depend on several factors such as the script's execution time, the pipeline depth, and the parallelizability class under which a command falls. 
%\kk{Do we need to mention this last sentence here? Without context it is pretty difficult for anyone to get something out of it.}

@@

The core of \sys is an abstract dataflow graph (DFG) model that is used as the intermediate representation on which \sys performs optimizations.
%% representation that is expressive enough to model data parallelism in shell programs.
%% support a large subset of shell programs.\nv{Immediate Q: How Large? Which programs are not supported? Why?}
\sys first lifts sections of the input script to the DFG
representation, it performs transformations to expose parallelism, and
then instantiates each DFG back to a parallel shell script.  A
fundamental difference with other DFG models is that it encodes the
order in which a node reads its inputs, which in turn enables a set of
graph transformations that can be iteratively applied to expose
parallelization opportunities for \tsta and \tpur commands.
%% data parallelism as task parallelism.\nv{What does this mean? What if they are fundamentally different in the reivewer's mind? Example?}
%% These transformations can then be applied in an iterative way, optimizing the program to utilize available computational resources. 
In \Cref{graph-components} we define the DFG model and describe the
correspondence with shell scripts, and in \Cref{ir:transformations} we
describe the graph transformations that \sys performs.
